Paper_analyses

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
kmeans on unnagregted data
this includes multiple trials p[er subject the result overall is similar to the aggregated data but the same stimuli can endup beogn assigned to multiple clusters, becauyse every opccurence of the same stimuli is treated as indeopendent

# aggregate for clustering first
clustering_agg <- clustering%>%
  group_by(stimIAPS2, stimDescription)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

@@

@@

clustering_agg<- subset(clustering_agg, !is.na(stimDescription))
colnames(clustering_agg)
clust_dataset = clustering_agg[c(20,24,25)]

@@

>>>>

# aggregate for clustering first

clustering$AlexGroup<- if_else(clustering$TAS> median(clustering$TAS, na.rm = TRUE), "High", "Low")

clustering_agg <- clustering%>%
  group_by(stimIAPS2, stimDescription)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_agg2 <- clustering%>%
  group_by(stimIAPS2, stimDescription,AlexGroup)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

@@

clustering_agg2<- clustering_agg2%>%
  ungroup()%>%
  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
  mutate(pup_basCor_z = scale(pup_basCor, center  = TRUE, scale= TRUE))

@@

clustering_agg<- subset(clustering_agg, !is.na(stimDescription))

clustering_agg$AlexGroup<- if_else(clustering_agg$TAS> median(clustering_agg$TAS, na.rm = TRUE), "High", "Low")
colnames(clustering_agg)
clust_dataset = clustering_agg[c(20,24,25)]

@@

Let's do on the unnagregates data

```{r}
colnames(clustering_agg)
colnames(clustering)

clustering2<- subset(clustering, !is.na(stimDescription))

# K-Means Clustering

colnames(clustering2)
clust2_dataset = clustering2[c(24,2,1,7:11,18,19)]

# Using the elbow method to find the optimal number of clusters
set.seed(6)
wcss2 = vector()
View(clust2_dataset)
clust2_dataset_nona<- na.omit(clust2_dataset)

for (i in 1:10) wcss2[i] = sum(kmeans(clust2_dataset_nona[,c(1:3)], i)$withinss)
plot(1:10,
     wcss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS')

# Fitting K-Means to the dataset
set.seed(29)
kmeans2 = kmeans(x = clust2_dataset_nona[,c(1:3)], centers = 3)
y_kmeans2 = kmeans2$cluster

clust2_dataset_nona$y_kmeans2 <- y_kmeans2

clust2_dataset_nona%>%
  ggplot(aes(as.factor(y_kmeans2), ArousalMean))+
  # geom_point()+
  stat_summary(geom = 'pointrange')

clust2_dataset_nona%>%
  ggplot(aes(as.factor(y_kmeans2), ValenceMean))+
  # geom_point()+
  stat_summary(geom = 'pointrange')

?car::scatter3d
View(clustering_agg)

clust2_dataset_nona$y_kmeans2<- as.factor(as.character(clust2_dataset_nona$y_kmeans2))
car::scatter3d(clust2_dataset_nona$log_Bio_CDA.PhasicMax_z, 
          clust2_dataset_nona$Bio_Mean_HR_dif, 
          clust2_dataset_nona$pup_basCor,
          fit = "smooth",
          # point = FALSE,
          # ellipsoid = TRUE,
          surface = FALSE,
          # groups = clust2_dataset_nona$y_kmeans2,
          point.col = clust2_dataset_nona$y_kmeans2
          )

pca_res2 <- prcomp(clust2_dataset_nona[,c(1:3)])
plot_data2 <- cbind(as.data.frame(pca_res2$x[, 1:2]), labels = clust2_dataset_nona$y_kmeans2)

ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
  # geom_point()
  geom_text(aes(label= clust2_dataset_nona$stimDescription))

summary(pca_res2)
```
